The effects of binarity on planet occurrence rates measured by transit surveys

### 2017-11-14 paper/model_2.tex
improved mass ratio distribution plot

\begin{figure}[!tb]
    \centering
    \includegraphics[width=0.6\textwidth]{figures/q_distribn_mag_limited.pdf}
    \caption{
        The distribution of the mass ratio for a magnitude limited sample of 
        binary stars. The underlying mass ratios are drawn from a uniform 
        distribution in a volume-limited sample, quite similar to that of 
        Raghavan 
        et al. (2010)'s Fig. 13.
        The entire bias can be understood analytically 
        (Eq.~\ref{eq:Malmquist_bias}).
        {\bf todo: make y axis label p(secondary with q).}
    }
    \label{fig:q_distribn_mag_limited}
\end{figure}

@@

There is also a Malmquist bias in Eq.~\ref{eq:model2_rate_density}, hidden 
away in the numbers of selected stars.
This is because the selected sample at a fixed planet radius and period is 
magnitude-limited.
Given a binary, the probability of drawing a mass ratio $q$ in a 
magnitude-limited sample scales as
\begin{equation}
p({\rm draw\ }q | {\rm system\ is\ binary}) \propto q^\beta (1+q^\alpha)^{3/2}
\label{eq:Malmquist_bias}
\end{equation}
where $q^\beta$ is the volume-limited probability of drawing a binary of mass 
ratio $q$, and the latter term is the Malmquist bias.
We show the magnitude-limited mass ratio distribution for the $\beta=0$ case 
in Fig.~\ref{fig:q_distribn_mag_limited}.
We emphasize that in Monte Carlo simulations of transit surveys, it is 
important to draw binaries from the correctly biased mass-ratio distribution 
(e.g., Bakos et al 2012, Sullivan et al 2015, Guenther et al 2017).

>>>>

\begin{figure}[!tb]
    \centering
    \includegraphics[width=0.6\textwidth]{figures/mass_ratio_distribution.pdf}
    \caption{
        The mass ratio distribution for a magnitude-limited sample of 
        binary stars, in which the underlying volume-limited distribution is 
        uniform (quite similar to {\it e.g.}, Raghavan et al. (2010)'s 
        Fig.~16).
        The entire bias can be understood analytically 
        (Eq.~\ref{eq:Malmquist_bias}).
    }
    \label{fig:q_distribn_mag_limited}
\end{figure}

@@

There is also a Malmquist bias in Eq.~\ref{eq:model2_rate_density}, hidden 
away in the numbers of selected stars.
This is because the selected sample at a fixed planet radius and period is 
magnitude-limited.
Given a binary, the probability of drawing a mass ratio $q$ in a 
magnitude-limited sample scales as
\begin{equation}
p({\rm draw\ }q\,|\,{\rm system\ is\ binary}) \propto q^\beta 
(1+q^\alpha)^{3/2}
\label{eq:Malmquist_bias}
\end{equation}
where $q^\beta$ is the volume-limited probability of drawing a binary of mass 
ratio $q$, and the latter term is the Malmquist bias.
We show the magnitude-limited mass ratio distribution for the $\beta=0$ case 
in Fig.~\ref{fig:q_distribn_mag_limited}.
We emphasize that in Monte Carlo simulations of transit surveys, it is 
important to draw binaries from the correctly biased mass-ratio distribution 
(e.g., Bakos et al 2012, Sullivan et al 2015, Guenther et al 2017).
